Specific leaf mass explains difference in biomass partitioning between woody plant functional types

### 2014-10-21 manuscript/draftpaper.Rnw
Found very minor effects of MAT on LMF, added to Fig 9, and MAP panel. smoothplotbypft can do lm instead of gam.

 Unlike \cite{reich_temperature_2014}, we found no effect of mean annual temperature on the scaling of leaf biomass with woody biomass (Fig.~\ref{fig:figureSI9}).

@@

 We found no effects of climate on anything, when analyzed in addition to PFT. This means that climate-related differences are captured by a shift in PFT (see also Fig.~\ref{figure1}, showing PFTs occupy different parts of the climate space). Our results contrast with those of \cite{reich_temperature_2014} but they studied whole-stand biomass, not individual plant biomass. So perhaps this means the climate effects are on stand density not individual plant effects. No effect of climate is good news for models that parameterize the globe by PFT, as this seems sufficient, based on our dataset. Are there experimental data that show temperature effects on allocation? What about water availability?

>>>>

 Unlike \cite{reich_temperature_2014}, we found only very weak effects of mean annual temperature the scaling of leaf biomass with woody biomass (Fig.~\ref{fig:figureSI9}). The size-invariant relationship was only significant for deciduous angiosperms, but it was a very weak correlation that explained very little additional variation. These results were confirmed with a mixed-effects model of MF vs. MS, with MAT and PFT as covariates (see Table XXX). We found no significant effects of mean annual precipitation of leaf-woody biomass relationships (Table XXX).

@@

 We found no appreciable effects of climate on anything, when analyzed in addition to PFT. This means that climate-related differences are captured by a shift in PFT (see also Fig.~\ref{figure1}, showing PFTs occupy different parts of the climate space). Our results contrast with those of \cite{reich_temperature_2014} but they studied whole-stand biomass, not individual plant biomass. So perhaps this means the climate effects are on stand density not individual plant effects. No effect of climate is good news for models that parameterize the globe by PFT, as this seems sufficient, based on our dataset. Are there experimental data that show temperature effects on allocation? What about water availability?
